Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
Adding NMSE Errors Definition
✅ Citation-rich Practical Deployment for Deep Learning-Based CSI Feedback Systems: Generalization Challenges and Enabling Techniques

@@

@@

>>>>

Lu \textit{et al.} \cite{prac2024} identify key challenges including channel distribution shifts and propose an alternating optimization framework with online knowledge-review to enhance adaptability. Their solution improves NMSE by 4.3 dB in unseen environments compared to conventional static models.

@@

The reconstruction quality is evaluated using the Normalized Mean Square Error (NMSE):
\[
\text{NMSE} = \mathbb{E}\left\{\frac{\|\tilde{\mathbf{H}}_f - \hat{\tilde{\mathbf{H}}}_f\|_F^2}{\|\tilde{\mathbf{H}}_f\|_F^2}\right\},
\]
where $\|\cdot\|_F$ denotes the Frobenius norm and $\mathbb{E}\{\cdot\}$ represents expectation over the dataset.

@@

	\bibitem{prac2024}
    Z. Lu, Y. Dong, H. He, S. Jin, and G. Y. Li, 
    ``Practical Deployment for Deep Learning-Based CSI Feedback Systems: Generalization Challenges and Enabling Techniques,''
    \emph{IEEE Wireless Communications}, 
    vol. 31, no. 2, pp. 72--79, 
    Apr. 2024, 
    doi: 10.1109/MWC.001.2300223.
